NumPy---Array Computation for Python

### 2019-12-20 body.tex
Add LSST reference

%NumPy is the fundamental array computation library for the Python
%ecosystem \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
Since its first stable release in October 2006, NumPy has unified
the scientific Python community and now underpins almost every library
that does numerical computation, including SciPy\cite{virtanen2019scipy},
pandas\cite{mckinney-proc-scipy-2010}, scikit-learn\cite{pedregosa2011scikit},
and scikit-image\cite{vanderwalt2014scikit}.
Not surprisingly, many important scientific research projects and
results crucially rely on NumPy.
It plays an essential role in many research analysis pipelines in
fields as diverse as physics, biology, astronomy, neuroscience,
material science, engineering, and chemistry.
% w/ citations
In particular, NumPy played a fundamental role in discovering
gravitational waves\cite{pycbc}, imaging black
holes\cite{eht-imaging}, and exploring the solar system (... Kepler? https://ui.adsabs.harvard.edu/abs/2012ascl.soft08004S/abstract).

>>>>

%NumPy is the fundamental array computation library for the Python
%ecosystem \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
Since its first stable release in October 2006, NumPy has unified
the scientific Python community and now underpins almost every library
that does numerical computation, including SciPy\cite{virtanen2019scipy},
pandas\cite{mckinney-proc-scipy-2010}, scikit-learn\cite{pedregosa2011scikit},
and scikit-image\cite{vanderwalt2014scikit}.
Not surprisingly, many important scientific research projects and
results crucially rely on NumPy.
It plays an essential role in many research analysis pipelines in
fields as diverse as physics, biology, astronomy, neuroscience,
material science, engineering, and chemistry.
% w/ citations
In particular, NumPy played a fundamental role in discovering
gravitational waves\cite{pycbc}, imaging black
holes\cite{eht-imaging}, and exploring the solar system \cite{jenness2018lsst}.
